\chapter{Literature Review}\label{ch:literatureoverview}
The use of technology into healthcare systems has witnessed remarkable progress in recent years.The management of medical reports, a critical aspect of patient care  has become a focal point for innovation. In this section, we review existing literature on the utilization of Optical Character Recognition (OCR) and Artificial Intelligence (AI) technologies in healthcare settings, with a specific focus on medical report scanning applications.
 \subsection*{AI for Analyzing Medical Information:}
Using AI in healthcare has changed how we analyze medical information, helping us understand things better and make decisions. AI computer with deep learning models, have shown they're really good at putting medical information into categories, picking out important parts, and explain them. Zhang and their team (in 2020) \cite{zhang2020deep} showed that AI can put medical images into groups accurately, which could help classify images automatically. Also, AI with natural language processing or NLP has been used to pull organized information out of messy medical text . Liu and others (in 2019)\cite{liu2019comparison} worked on this.
\subsection*{Apps for Sorting and Organizing Medical Reports:}
New mobile apps that focus on sorting and organizing medical reports are changing how we manage healthcare papers. These apps use OCR and AI to make things smoother and improve how healthcare is given. A study by Smith and their team (in 2021)\cite{smith2021improving} showed that one of these apps was easy to use and worked well. It helped healthcare workers scan and put medical reports into groups quickly, saving a lot of time and making data easier to get. These apps help doctors and nurses take care of patients better and make smarter choices.
\newline
\newline \noindent
In summary, the use of OCR and AI technologies within medical report scanning and organization applications holds immense promise for healthcare efficiency and patient care. The reviewed literature emphasizes the significance of these technologies in digitizing medical records, categorizing reports, and extracting meaningful insights. Building upon this foundation, our proposed Medical Report Scanning  App seeks to use these technologies to create a seamless, user-friendly platform that empowers healthcare professionals and patients .




